\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-09 paper_resources/doc/paper.tex
Results were wrong on the SRBEnch site!!!

\begin{table}[!htb]
	\caption{Comparison without noise}\label{tab:comp_noise0}
	\centering
	\begin{tabular}{l|rrr|rrr} \hline
		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
		\textsc{Rils-Rols}&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
		\textsc{AI-Feynman} &55.78&27.14&52.69&78.51&35.71&73.9\\
		\textsc{Gomea} &26.83&29.46&27.12&71.55&71.43&71.54\\
		\textsc{Afp-Fe} &26.98&20&26.23&59.05&28.57&55.77\\
		\textsc{Itea}&22.41&7.14&20.77&27.59&21.43&26.93\\
		\textsc{Afp}&21.12&15.18&20.48&44.83&25&42.69\\
		\textsc{Dsr}&19.72&19.64&19.71&25&14.29&23.85\\
		\textsc{Operon}&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
		\textsc{gplearn}&16.27&8.93&15.48&32.76&7.14&30\\
		\textsc{Sbp-Gp}&12.72&11.61&12.6&73.71&78.57&74.23\\
		\textsc{Eplex}  &12.39&8.93&12.02&46.98&21.43&44.23\\
		\textsc{Bsr}&2.48&0.89&2.31&10.78&21.43&11.93\\
		\textsc{Feat}&0&0.89&0.1&39.66&42.86&40\\
		\textsc{Ffx}&0&0&0&0&0&0\\
		\textsc{Mrgp}&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[!htb]
	\caption{Comparison with noise level 0.001}\label{tab:comp_noise0001}
	\centering
	\begin{tabular}{l|rrr|rrr} \hline
		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
		\textsc{Rils-Rols}&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
		\textsc{Dsr}&16.81&18.75&17.02&26.29&14.29&25\\
		\textsc{gplearn}&15.84&8.93&15.1&24.14&7.14&22.31\\
		\textsc{Afp-Fe}&15.95&6.43&14.92&57.76&28.57&54.62\\
		\textsc{Afp}&14.87&7.14&14.04&44.83&25&42.69\\
		\textsc{Eplex} &10.02&2.68&9.23&48.71&21.43&45.77\\
		\textsc{AI-Feynman}&1.49&13.73&2.81&9.73&35.71&12.53\\
		\textsc{Itea}&1.94&4.46&2.21&26.72&21.43&26.15\\
		\textsc{Gomea}&1.62&0.89&1.54&72.84&71.43&72.69\\
		\textsc{Operon}&0.34&0&0.31&\bf{81.9}&\bf{92.86}&\bf{83.08}\\
		\textsc{Ffx}&0.11&0&0.1&19.4&14.29&18.85\\
		\textsc{Feat}&0&0.89&0.1&13.79&50&17.69\\
		\textsc{Sbp-Gp}&0&0&0&62.07&53.57&61.15\\
		\textsc{Bsr}&0&0&0&7.76&14.29&8.46\\
		\textsc{Mrgp}&0&0&0&0.86&17.86&2.69\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[!htb]
	\caption{Comparison with noise level 0.01}\label{tab:comp_noise001}
	\centering
	\begin{tabular}{l|rrr|rrr} \hline
		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
		\textsc{Rils-Rols}&\bf{36.29}&\bf{22.14}&\bf{34.77}&\bf{64.91}&\bf{46.43}&\bf{62.92}\\
		\textsc{gplearn}&13.21&8.93&12.75&14.22&7.14&13.46\\
		\textsc{Dsr}&8.41&16.07&9.23&17.24&14.29&16.92\\
		\textsc{Eplex}&8.77&0&7.83&14.22&3.57&13.07\\
		\textsc{Afp}&7.11&0.89&6.44&8.19&7.14&8.08\\
		\textsc{Afp-Fe}&6.12&3.57&5.85&5.6&0&5\\
		\textsc{Itea}&0.11&0.89&0.19&1.72&10.71&2.69\\
		\textsc{AI-Feynman}&0&0.79&0.09&0&0&0\\
		\textsc{Operon}&0.09&0&0.08&0&0&0\\
		\textsc{Gomea}&0&0&0&0&0&0\\
		\textsc{Sbp-Gp}&0&0&0&0&0&0\\
		\textsc{Bsr}&0&0&0&0&0&0\\
		\textsc{Feat}&0&0&0&0&14.29&1.54\\
		\textsc{Ffx}&0&0&0&0&0&0\\
		\textsc{Mrgp}&0&0&0&0&0&0\\
		\hline
	\end{tabular}
\end{table}

>>>>

\begin{table}[!htb]
	\caption{Comparison without noise}\label{tab:comp_noise0}
	\centering
	\begin{tabular}{l|rrr|rrr} \hline
		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
		RILS-ROLS&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
		AIFeynman&55.78&27.14&52.65&78.51&35.71&73.83\\
		GP-GOMEA&26.83&29.46&27.12&71.55&71.43&71.54\\
		AFP\_FE&26.98&20&26.23&59.05&28.57&55.77\\
		ITEA&22.41&7.14&20.77&27.59&21.43&26.92\\
		AFP&21.12&15.18&20.48&44.83&25&42.69\\
		DSR&19.72&19.64&19.71&25&14.29&23.85\\
		Operon&16.55&11.43&16&86.21&\bf{92.86}&86.92\\
		gplearn&16.27&8.93&15.48&32.76&7.14&30\\
		SBP-GP&12.72&11.61&12.6&73.71&78.57&74.23\\
		EPLEX&12.39&8.93&12.02&46.98&21.43&44.23\\
		BSR&2.48&0.89&2.31&10.78&21.43&11.92\\
		FEAT&0&0.89&0.1&39.66&42.86&40\\
		FFX&0&0&0&0&0&0\\
		MRGP&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[!htb]
	\caption{Comparison with noise level 0.001}\label{tab:comp_noise0001}
	\centering
	\begin{tabular}{l|rrr|rrr} \hline
		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
		RILS-ROLS&\bf{42.93}&\bf{35}&\bf{42.08}&80.26&65&78.62\\
		AIFeynman&33.08&22.14&31.89&77.39&42.86&73.64\\
		AFP\_FE&21.9&15.71&21.23&52.16&35.71&50.38\\
		DSR&19.14&19.29&19.15&25.86&14.29&24.62\\
		AFP&19.66&13.57&19&44.4&21.43&41.92\\
		gplearn&16.99&9.29&16.16&31.9&7.14&29.23\\
		ITEA&14.57&7.14&13.77&27.59&21.43&26.92\\
		Operon&13.19&5&12.31&85.78&\bf{92.86}&86.54\\
		GP-GOMEA&11.03&7.14&10.62&70.26&71.43&70.38\\
		EPLEX&9.57&9.29&9.54&47.84&25&45.38\\
		SBP-GP&0.78&0&0.69&75.43&64.29&74.23\\
		BSR&0.6&0.71&0.62&10.34&14.29&10.77\\
		FFX&0&0&0&0&0&0\\
		FEAT&0&0&0&42.24&50&43.08\\
		MRGP&0&0&0&\bf{92.24}&85.71&\bf{91.54}\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[!htb]
	\caption{Comparison with noise level 0.01}\label{tab:comp_noise001}
	\centering
	\begin{tabular}{l|rrr|rrr} \hline
		& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
		Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
		RILS-ROLS&\bf{36.29}&\bf{22.14}&\bf{34.77}&64.91&46.43&62.92\\
		AFP\_FE&20.78&13.57&20&52.59&32.14&50.38\\
		DSR&18.97&18.57&18.92&26.29&14.29&25\\
		AFP&16.9&11.43&16.31&42.67&21.43&40.38\\
		gplearn&16.87&9.29&16.05&29.13&10.71&27.13\\
		AIFeynman&13.03&9.29&12.61&71.43&39.29&67.86\\
		EPLEX&8.71&4.29&8.23&56.03&21.43&52.31\\
		ITEA&7.84&6.43&7.69&27.59&21.43&26.92\\
		GP-GOMEA&5.09&1.43&4.69&73.71&71.43&73.46\\
		Operon&2.07&0.71&1.92&85.78&\bf{92.86}&86.54\\
		BSR&0.09&0&0.08&12.07&10.71&11.92\\
		SBP-GP&0&0&0&75&75&75\\
		FEAT&0&0&0&40.52&42.86&40.77\\
		FFX&0&0&0&2.59&3.57&2.69\\
		MRGP&0&0&0&\bf{91.81}&60.71&\bf{88.46}\\
		\hline
	\end{tabular}
\end{table}
